Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Reviewing problem description and leaving a comment

The main objective of this paper is to forecast sales for 
%FERGU: el objetivo es la herramienta o la predicción?
unpublished books for which no historical data are available. Instead, just some
%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
descriptive and variables known in advance related to the new book. In
order to do that, we have used a training dataset which includes
historical sales data for a big amount of books published in Spain for
several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends or 
promotions, that classical prediction methods can not deal with. %FERGU: por qué?
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method, will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it in his/her own prediction process.

>>>>

The main objective of this paper is to forecast sales for 
%FERGU: el objetivo es la herramienta o la predicción?
unpublished books for which no historical data are available. Instead, just some
%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
descriptive and variables are known in advance related to the new book. In
order to do that, we have used a training dataset which includes
historical sales data % (Paloma) so, have we or have we not historical data? It's all contradictory
 for a big amount of books published in Spain for
several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends, or 
promotions, that classical prediction methods can not deal with. %FERGU: por qué?
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it in his or her own prediction process.
